---
title: ""
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    theme: bootstrap
    logo: asu_university_horiz_rgb_white_600.png
    favicon: asu-favicon.ico
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

#This is where you can load packages, clean data, and do any other prep work.

```
library(usmap)
library(ggplot2)

Row {data-height=600}
-----------------------------------------------------------------------

```{r, out.width = "100%"}


selectInput("Type", label="Select Type", choices=c("A", "B"))

```



Page 1
============================================================================
Row {data-height=600}
-----------------------------------------------------------------------
### Geologic Map
```{r}
renderPlot({
library(usmap)
library(ggplot2)

plot_usmap(data = statepop, values = "pop_2015", lines = "red") + 
  scale_fill_continuous(
    low = "white", high = #5681b5, name = "Population (2015)", label = scales::comma
  ) + theme(legend.position = "right")

})

```

Row
-----------------------------------------------------------------------

### Density by State

```{r}
renderPlot({
  X = rnorm(100)
  hist(X)

})


```


Page 2
============================================================================
Row
-----------------------------------------------------------------------
### Plot2.1
```{r}
renderPlot({
  X = rnorm(100)
  plot(X)

})

```


Column {data-width=350}
-----------------------------------------------------------------------

### Plot2.2

```{r}
renderPlot({
  X = rnorm(100)
  plot(X)

})

```

### Plot2.3

```{r}
renderPlot({
  X = rnorm(100)
  plot(X)

})
```


Page 3
============================================================================

Row
-----------------------------------------------------------------------
### Plot 3.1
```{r}
renderPlot({
  X = rnorm(100)
  plot(X)

})
   
```


<style>

.navbar-logo img {
height: 48px;


}


.navbar-inverse {
  background-color: #353535;
  border-color: #353535;
  text-color: #ffffff;
    font-size: 16px;
    font-weight: bold;
    border: none;
}


.navbar-inverse .navbar-text {
  background-color: #353535;
  border-color: #353535;
  color: #ffffff;
    font-size: 16px;
    font-weight: bold;
    border: none;
}
.navbar-inverse .navbar-nav > li > a {
  background-color: #353535;
  border-color: #353535;
  color: #ffffff;
    font-size: 16px;
    font-weight: bold;
    border: none;
}
.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
  background: #1f1f1f;
    color: #ffb130;
    font-size: 16px;
    font-weight: bold;
    border: none;
}
.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  background: #1f1f1f;
    color: #ffb130;
    font-size: 16px;
    font-weight: bold;
    border: none;
}
.navbar-inverse .navbar-nav > .disabled > a,
.navbar-inverse .navbar-nav > .disabled > a:hover,
.navbar-inverse .navbar-nav > .disabled > a:focus {
  background: #1f1f1f;
    color: #ffb130;
    font-size: 16px;
    font-weight: bold;
    border: none;
}

body {
  padding-top: 0px;
}

.shiny-output-error { visibility: hidden; }
.shiny-output-error:before { visibility: hidden; }


</style>
